Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-12 paper/us_election_2020.qmd
changes

## Model Implication
Figure # shows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure # with the x axis limited from -10 to 10.

Combining figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.

@@

@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure # with the x axis limited from -10 to 10.

@@

```{r}
#| label: fig-conf
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
plot(
  political_preferences1,
  "areas"
)
```
```{r}
#| label: fig-conf_lim
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
#| 
model_plot <- plot(
  political_preferences1,
  "areas"
)
# Modify the x-axis limits
model_plot + xlim(-10, 10) +  # Adjust the limits as needed
  labs(x = "90% Credibility Interval")
```
## Credibility Interval

```{r}
# #| echo: false
# #| eval: true
# #| warning: false
# #| message: false
# #| label: fig-modelresults1
# #| fig-cap: "Credible intervals for predictors of support for Biden 1"
# 
# modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
#   labs(x = "90% credibility interval")
```

```{r}
# #| echo: false
# #| eval: true
# #| warning: false
# #| message: false
# #| label: fig-modelresults2
# #| fig-cap: "Credible intervals for predictors of support for Biden 2"
# # Create the model plot
# model_plot <- modelplot(political_preferences1, conf_level = 0.9)
# 
# # Modify the x-axis limits
# model_plot + xlim(-5, 5) +  # Adjust the limits as needed
#   labs(x = "90% Credibility Interval")
```

>>>>

@@

@fig-modelresults1 (see @sec-credibility-interval) inshows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure # with the x axis limited from -10 to 10.

@@

```{r}
#| label: fig-conf
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
plot(
  political_preferences1,
  "areas"
)
```
```{r}
#| label: fig-conf_lim
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
#| 
model_plot <- plot(
  political_preferences1,
  "areas"
)
# Modify the x-axis limits
model_plot + xlim(-10, 10) +  # Adjust the limits as needed
  labs(x = "90% Credibility Interval")
```
## Credibility Interval {#sec-credibility-interval}

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-modelresults1
#| fig-cap: "Credible intervals for predictors of support for Biden 1"

modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
 labs(x = "90% credibility interval")
```

```{r}
 #| echo: false
 #| eval: true
 #| warning: false
 #| message: false
 #| label: fig-modelresults2
 #| fig-cap: "Credible intervals for predictors of support for Biden 2"
 # Create the model plot
 model_plot <- modelplot(political_preferences1, conf_level = 0.9)

 # Modify the x-axis limits
 model_plot + xlim(-10, 10) +  # Adjust the limits as needed
   labs(x = "90% Credibility Interval")
```
